### 2014-01-29 docs/paper/paper.tex
point form notes under certain other sections

@@

\subsubsection{VC707}

\subsubsection{Ethernet}

@@

% quick description of what that involves

@@

\subsection{Limitations}
\subsection{Future work \& extensions}

>>>>

\begin{itemize}
\item encoder instruction buffer size limits number of decoded values that can be encoded
\item dimensional restrictions -- 1D, 2D population units
\item four decoded values per population -- using more will create copies of populations to accommodate extra decoders
\end{itemize}

@@

\begin{itemize}
\item VC707 board
\item resources available -- BRAM, DSP
\item implemented design -- number of population units, DV buffers
\item FPGA resources utilized; maximum theoretical design size
\item clock speed and implications of this
\item Ethernet communication for control and I/O -- maximum channel capacity in terms of DVs
\end{itemize}

@@

\begin{itemize}
\item quick description of Nengo
\item Nengo ensembles are hardware populations
\item Nengo connections are hardware encoders and decoders
\item Nengo nodes and probes are hardware I/O endpoints
\item compiler functions: calculate principal components, map populations to PCs, calculate decoders and encoders,
calculate encoder schedule, create programming file
\item Nengo will then program the board and communicate with it during simulation
\end{itemize}

@@

\subsection{Limitations}

\subsection{Future work \& extensions}

\begin{itemize}
\item board-to-board communication for larger networks
\item increase design size by using off-chip memory (DDR3)
\item better network stack to allow control and I/O over common protocols e.g. UDP
\end{itemize}
